Capstone Movielens Report

### 2025-05-23 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
UMGYE Model, Support functions described.

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [UMGE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L1) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We have already explained that in the [User+Movie Effect Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

#### `train_user_movie_genre_effect.cv` Function {#func.train_user_movie_genre_effect.cv}
\

We use the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) function to train the current model using the _5-Fold Cross Validation_ method. Below, we provide a slightly simplified version of the source code of that function:
```{r eval=FALSE}
train_user_movie_genre_effect.cv <- function(lambda = 0){
  # ...

@@

Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
```{r, eval=FALSE}
cv.UMG_effect <- train_user_movie_genre_effect.cv()
```
```{r}
str(cv.UMG_effect)

>>>>

::: {.noteblock data-latex=""}
Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We have already explained that in the [UME Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

@@

#### [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) Function {#func.train_user_movie_genre_effect.cv}
\

We use this function, defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) script, to train the current model using the _5-Fold Cross Validation_ method. Below, we provide a slightly simplified version of the source code of that function:
```{r eval=FALSE}
train_user_movie_genre_effect.cv <- function(lambda = 0){
  # ...

@@

Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
```{r, fn.train_user_movie_genre_effect.cv,   eval=FALSE}
cv.UMG_effect <- train_user_movie_genre_effect.cv()
```
```{r, hist.cv.UMG_effect }
str(cv.UMG_effect)

### 2025-05-23 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
UMGYE Model, Support functions described.

If we define $\gamma(q)$ as the _year effect_ for the year (which is denotes by $q$ here) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:

\begin{equation}
Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(q) + \varepsilon_{i,j}
(\#eq:UMGYE-model)
\end{equation}

Therefore, the formula \@ref(eq:genre-effect) for calculation the prediction of a _genre effect_ as a residual, for a _year effect_ 
$$
\hat{\gamma}(q) = \gamma(q) + \varepsilon_{i,j}
$$

@@

\begin{equation}
\hat{\gamma}(q) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
(\#eq:year-effect)
\end{equation}

@@

::: {.noteblock data-latex=""}
Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We have already explained that in the [UMGYE Effect Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
\

```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
Note
:::

#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
\

```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
Note
:::

#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
\

```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
Note
:::

#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
\

```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
Note
:::

#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
\

```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
Note
:::

@@

  if(lambda == 0) put_log("Function `calc_date_general_effect`:
Computing Date Global Effect for given Train Set data...")
  else put_log1("Function `calc_date_general_effect`:
Computing Date Global Effect for lambda: %1...",
                lambda)
  dg_effect <- train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    mutate(resid = rating - (mu + a + b + g)) |>
    # filter(!is.na(resid)) |>
  group_by(days) |>
    summarise(de = mean_reg(resid, lambda), 
              year = mean(year))
  dg_effect
}
```

::: {.noteblock data-latex=""}
The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub.
:::

#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) Function {#func.calc_UMGY_effect}
\

@@

The function accepts the only parameter `date_general_effect`, which is a data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) function described above.

@@

::: {.noteblock data-latex=""}
The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) script on _GitHub.
:::

#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) Function {#func.train_UMGY_effect}
\

@@

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) script on _GitHub.
:::

#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L88) Function {#func.train_UMGY_effect.cv}
\

@@

#### `calc_UMGY_effect_MSE` Function
\

The source code of the function [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ is provided below:
```{r eval=FALSE}
```

@@

#### `calc_UMGY_effect_MSE.cv` Function
\

The source code of the function [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation MSE_ result of the _UMGYE Model_ is provided below:
```{r eval=FALSE}
```

#### `calc_UMGY_effect_RMSE` Function
\

The source code of the function [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UMGYE Model_ for the given _Test Set_ is provided below:

```{r eval=FALSE}
```

#### `calc_UMGY_effect_RMSE.cv` Function { #func.calc_UMGY_effect_RMSE.cv }
\

The source code of the function [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UMGYE Model_ is provided below:

```{r eval=FALSE}
```

@@

>>>>

If we define $\gamma(r)$ as the _year effect_ for the year (here denotes by $r$) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:

\begin{equation}
Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(r) + \varepsilon_{i,j}
(\#eq:UMGYE-model)
\end{equation}

Therefore, the formula \@ref(eq:genre-effect) for calculation the prediction of a _genre effect_ as a residual, for a _year effect_ 
$$
\hat{\gamma}(r) = \gamma(r) + \varepsilon_{i,j}
$$

@@

\begin{equation}
\hat{\gamma}(r) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
(\#eq:year-effect)
\end{equation}

@@

::: {.noteblock data-latex=""}
Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We have already explained that in the [UME Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

@@

  if(lambda == 0) put_log("Function `calc_date_general_effect`:
Computing Date Global Effect for given Train Set data...")
  else put_log1("Function `calc_date_general_effect`:
Computing Date Global Effect for lambda: %1...",
                lambda)
  dg_effect <- train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    mutate(resid = rating - (mu + a + b + g)) |>
  group_by(days) |>
    summarise(de = mean_reg(resid, lambda), 
              year = mean(year))
  dg_effect
}
```

::: {.noteblock data-latex=""}
The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub_.
:::

##### Return

A data structure containg information about _Date General Effect_.

#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) Function {#func.calc_date_general_effect.cv}
\

This is a helper function that calculates the _date general effect_ of the user ratings using the _5-Fold Cross Validation_ method and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect.cv](#func.train_UMGY_effect.cv)) described below.
The following is a simplified version of the function's source code:
```{r eval=FALSE}
calc_date_general_effect.cv <- function(lambda = 0){
  if (is.na(lambda)) {
    stop("Function: calc_date_general_effect.cv
`lambda` is `NA`")
  }

  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
    cv_fold_dat$train_set |> calc_date_general_effect(lambda)
  })
  str(date_general_effect_ls)

  date_general_effect_united <- union_cv_results(date_general_effect_ls)

  date_general_effect_united |>
    group_by(days) |>
    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
}
```

::: {.noteblock data-latex=""}
The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) script on _GitHub_.
:::

##### Return

A data structure containg information about _Date General Effect_ as result of _5-Fold Cross Validation_.

#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) Function {#func.calc_UMGY_effect}
\

@@

The function accepts the only parameter `date_general_effect`, which is a data structure returned by any of the following functions described above:

  - [calc_date_general_effect](#func.calc_date_general_effect);
  - [calc_date_general_effect.cv](#func.calc_date_general_effect.cv).

@@

::: {.noteblock data-latex=""}
The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) script on _GitHub_.
:::

##### Return

A data structure containg information about _User+Movie+Genre+Year (UMGY) Effect_.

#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) Function {#func.train_UMGY_effect}
\

@@

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) script on _GitHub_.
:::

##### Return

A data structure containg information about _User+Movie+Genre+Year (UMGY) Effect_.

#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) Function {#func.train_UMGY_effect.cv}
\

@@

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) function is also available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) script on _GitHub_.
:::

##### Return

A data structure containg information about _User+Movie+Genre+Year (UMGY) Effect_.

#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) Function
\

The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.

  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
  - **UMGY_effect:** A data structure returned by any of the following functions described above:
    - [calc_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_MSE <- function(test_set, UMGY_effect){
  test_set |>
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(UMGY_effect, by='year') |>
    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
    pull(resid) |> mse()
}
```

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) script. 
:::

@@

#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) Function
\

The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.

The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:

  - [calc_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
  start <- put_start_date()
  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
  })
  put_end_date(start)
  put_log1("Function: calc_UMGY_effect_MSE.cv
Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
           CVFolds_N)

  mean(UMGY_effect_MSEs)
}

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) script. 
:::

#### [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) Function
\

The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.

  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
  - **UMGY_effect:** A data structure returned by any of the following functions described above:
    - [calc_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_RMSE <- function(test_set, UMGY_effect){
  mse <- test_set |> calc_UMGY_effect_MSE(UMGY_effect)
  sqrt(mse)
}
```

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) script. 
:::

@@

#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) Function
\

The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.

The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:

  - [calc_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
           CVFolds_N, 
           UMGY_effect_RMSE)

  UMGY_effect_RMSE
}
```

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) script. 
:::
